Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-10-21 Report/convergence_centralized.tex
conv modified

To prove the convergence of the transmit, receive beamformers, and the objective values of the centralized algorithms in \eqref{eqn-6} and \eqref{eqn-mse-1}, we will show that the following conditions are satisfied by the centralized formulations.
\begin{itemize}
	\item[(a)] The function should be bounded below
	\item[(b)] The feasible set should be a compact set
	\item[(c)] The sequence of the objective values should be \review{strictly} decreasing in each iteration
	\item[(d)] Uniqueness of the minimizer, \textit{i.e.}, the transmit and the receive beamformers should be unique in each iteration.
\end{itemize}
The conditions (a) (b) and (c) are required for the convergence of the objective values generated by the iterative algorithm. Since the feasible set is not fixed in each iteration, we require the condition (d) to prove the convergence of the objective function by enforcing unique transmit precoders and receive beamformer in each step of the iterative algorithm. Assuming conditions (a), (b) and (c) are satisfied, using \cite[Th. 3.14]{rudin1964principles}, we can show that the bounded and strictly decreasing objective sequence has a unique minimum in the feasible set. Finally, we use the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1} to show that \reviewF{every limit point of a convergent subsequence is a stationary point of the nonconvex problem} in \eqref{eqn-6} and \eqref{eqn-mse-1}, since the compact feasible set can have multiple limit points \cite{bertsekas1999nonlinear}.

Before proceeding further, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where \me{g_2}, \me{\hat{f}} are convex and \me{h} is a linear function. Let \me{g_0,g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not on both. The constraint in \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3}. Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
	\begin{equation}
	\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
	\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

To solve \eqref{con}, we adopt \ac{AO} by fixing a block of variables and optimize for others \cite{bezdek2002some}. However, after fixing the variable \me{\my}, the problem is still nonconvex due to the constraint \eqref{con-dc}. To overcome this issue, we resort to \ac{SCA} principle presented in \cite{lanckriet2009convergence,scutari_1,scutari-1} by relaxing \eqref{con-dc} by a sequence of convex subsets. Since it involves two nested iterations, we denote the \ac{AO} step by a superscript \me{(i)} and the \ac{SCA} iteration by a subscript \me{k}. Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k|\my}{i}} be a solution for stacked \me{\mx} and \me{\gamma} obtained in the \eqn{\ith{k}} \ac{SCA} step and in the \eqn{\ith{i}} \ac{AO} step for fixed \me{\my}. Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be a solution obtained for \me{\mx} and \me{\gamma} when the objective sequence converges in \eqn{\ith{i}} \ac{AO} step.

@@

since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the unique solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

\review{Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured. It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}
\begin{comment}
\begin{equation} \label{strict_monotonicity}
f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
\end{equation}

@@

In order to discuss the convergence of the sequence of iterates, let us define a global index \eqn{t}, which includes \ac{SCA} indexing \eqn{k} and \ac{AO} iteration count \eqn{i} corresponding to both transmit and receive beamformer updates. Using this global indexing, let us define \eqn{\ma^{t}} as a vector formed by stacking the solution obtained at the \eqn{\ith{k}} \ac{SCA} update of the \eqn{\ith{i}} \ac{AO} step as \eqn{[\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]}. Note that for some other \eqn{t}, say, \eqn{t^\prime > t}, such that \eqn{\ma^{t^\prime} \triangleq [\iter{\mx}{}{i},\iter{\my}{k}{i},\iter{\mz}{k|\mx}{i}]}. Therefore, \eqn{\ma^t} corresponds to all solutions obtained by the algorithm in each iteration.

Now, using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the whole sequence \eqn{\{{f}(\ma^t)\}} converges and \eqn{\forall t, \; \hat{f}(\ma^t) \leq f(\ma^t)}, and therefore \eqn{\hat{f}(\ma^t)} also converges. However, it is not the case with the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm, since there can be two different convergent subsequences, say, \eqn{\{\ma^{t_i} | i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} | k = 0,1,\dotsc\}}, such that
\begin{equation}
\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k}).
\end{equation}

Due to the existence of multiple limit points, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. Note that since the objective sequence \eqn{\{f(\ma^t)\}} converges to, say, \eqn{f(\bar{\ma})}, for some \eqn{\bar{\ma}}, then we show that \eqn{\bar{\ma}} is a stationary point. To show that, let us consider a subsequence \eqn{\{\ma^{t_j} | j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}. It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
\begin{equation}
f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
\end{equation}
Now, by taking the limit as \eqn{j \rightarrow \infty}, we obtain
\begin{equation}
f(\bar{\ma}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}})
\end{equation}
therefore, \eqn{\bar{\ma}} is a stationary point. The above discussion also includes the \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} \cite[Prop. 2.7.1]{bertsekas1999nonlinear}.

>>>>

Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear. Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly. The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively. Other convex constraints are addressed by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
	\begin{equation}
		\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
	\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

Now, to show the convergence of the sequence of objective values generated by the centralized algorithm Algorithm \ref{algo-1} for the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}, we require the following.
\begin{itemize}
	\item[(a)] Objective function should be bounded below
	\item[(b)] Feasible set should be a compact
	\item[(c)] Sequence of objective values should be strictly decreasing
	\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}. However, to ensure strict monotonicity of the objective sequence, we need condition (d). Assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, we can ensure the convergence of objective sequence \cite[Th. 3.14]{rudin1964principles}. Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates is a stationary point of the nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}, where iterates correspond to stacked vector of all optimization variables.

Before proceeding further, we denote the representations used in the following proof with respect to Algorithm \ref{algo-1}. Since it involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} correspond to the stacked vector all transmit precoders, receive beamformers, and other optimization variables, such as \me{\beta_{l,k,n},\gamma_{l,k,n}} or \eqn{t_{l,k,n},\epsilon_{l,k,n}} respectively. Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k}{i}} be the solution obtained in \eqn{\ith{i}} \ac{AO} step of \eqn{\ith{k}} \ac{SCA} iteration for the optimization variables \me{\mx} and \me{\gamma} with fixed \me{\my}. %We denote \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} as the solution obtained for \me{\mx} and \me{\mz} when the sequence of objective values converges in \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}. Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}.

@@

since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

\review{Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured. It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}

\begin{comment}
\begin{equation} \label{strict_monotonicity}
f(\iter{\mbf{z}}{k}{i}) - f(\iter{\mbf{z}}{k+1}{i}) \geq \nabla f(\iter{\mbf{z}}{k+1}{i})^\tran (\mbf{z}_{k}^{(i)} - \iter{\mbf{z}}{k+1}{i}) + \frac{m}{2} \, \|\mbf{z}_{k+1}^{(i)} - \iter{\mbf{z}}{k}{i}\|^2  \eqspace
\end{equation}

@@

In this section, we discuss the convergence of the sequence of iterates generated by the iterative algorithm. In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}. Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}. The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.

Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges. Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}. However, similar claim cannot be made on the convergence of sequence of iterates \eqn{\{\ma^t\}}, since there can be two different convergent subsequences of \eqn{\{\ma^t\}}, say, \eqn{\{\ma^{t_i} \, | \, i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} \, | \, k = 0,1,\dotsc\}}, such that
\begin{equation}
\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k})
\end{equation}
therefore, \eqn{\{\ma^t\}} is not convergent. The existence of a convergent subsequence is guaranteed by \cite[Th. 3.6]{rudin1964principles}, since \eqn{\{\ma^t\}} is a sequence in the compact set \eqn{\mc{F}}, and therefore bounded.

Since the sequence of iterates \eqn{\{\ma^t\}} may not be convergent, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To prove the stationarity of a limit point \eqn{\bar{\ma}}, let us consider that \eqn{\{f(\ma^t)\}} converges to \eqn{f(\bar{\ma})}, then we show that \eqn{\bar{\ma}} is a stationary point. To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to the limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}. It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
\begin{equation} \label{seq_mon}
f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
\end{equation}
Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of the objective function \eqn{f}, we obtain
\begin{equation}
\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma})
\end{equation}
and moreover, it follows
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
\end{equation}
where \eqn{\mc{Q}} is the feasible set defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}. Eq. \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}. Hence, the limit point of a convergent subsequence \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.

%The above discussion also considers \ac{AO} step, since in between each \ac{AO} update, the objective sequence is strictly monotonic \eqref{fixed_point} and it follows \cite[Prop. 2.7.1]{bertsekas1999nonlinear}.
